### 2025-04-08 download-football-data.qmd
20250407 - edits

In this case, I arrange the data by player using `display_name`.
You could arrange by `gsis_id` (or any other variable, for that matter), but `gsis_id` is fairly unintelligible by itself.
For instance, here are the first 6 players by ID according to `gsis_id`:

@@

Note how it is more clear, at a glance and without additional, who these players are.

>>>>

In this case, I arrange the data by player using `display_name`.
You could arrange by `gsis_id` (or any other variable, for that matter), but `gsis_id` is fairly unintelligible by itself.
For instance, here are the first six players by ID according to `gsis_id`:

@@

Note how it is more clear, at a glance and without additional information, who these players are.
